Variants of G\"{o}del's Ontological Proof \\ in a Natural Deduction Calculus

### 2016-11-08 Papers/InProgress/NaturalDeduction/GodProof-ND.tex
Improve acknowledgements

\paragraph{Acknowledgements:} This work was supported by an Stipendium of the \"Osterreichische Akademie der Wissenschaften (APART). We thank Christoph Benzm\"uller for collaborations on several related works.

>>>>

\paragraph{Acknowledgements:} We thank Padre Edvaldo (from Piracicaba, Brazil) for assisting Bruno and his family in a moment of need. His help triggered the beginning of this work in 2013. We are grateful to Christoph Benzm\"uller for collaborations on several related works. This work was supported by an Stipendium of the \"Osterreichische Akademie der Wissenschaften (APART).
